\begin{thebibliography}{99}
\label{bibliography}
\setlength{\itemsep}{1.5pt plus 2.0pt minus 1.4pt}
\setlength{\parsep}{0pt}
\setlength{\parskip}{0pt}
\vspace{-6pt}
\bibitem{nswtdr} ATLAS New Small Wheel Technical Design Report. \href{http://cds.cern.ch/record/1552862}{\color{blue}\underline{ATLAS-TDR-020}}.
 \href{https://cds.cern.ch/record/2272355}{\color{blue}\underline{ATL-COM-MUON-2017-036}}.
\bibitem{brian} B.~Clark {\it et al,} An Algorithm for Micromegas Segment
 Reconstruction in the Level-1 Trigger of the New Small Wheel. 
\href{https://cds.cern.ch/record/1706160}{\color{blue}\underline{ATL-COM-UPGRADE-2014-012}}.
\bibitem{steve} S.~Chan et. al. Micromegas Trigger Processor Algorithm Performance in Nominal, Misaligned, and Misalignment
 Corrected Conditions. \href{https://cds.cern.ch/record/2113121}{\color{blue}\underline{ATL-COM-UPGRADE-2015-033}}.
\bibitem{noisy} P.~Giromini {\it et al,} Performance of a Micromegas octuplet in the time  of noise.
 \href{https://cds.cern.ch/record/2277316}{\color{blue}\underline{ATL-COM-MUON-2017-036}}.
\bibitem{noiseless} P.~Giromini  {\it et al,} Performance of a Micromegas octuplet after removing the major cause of noise.
 \href{https://cds.cern.ch/record/2277316}{\color{blue}\underline{ATL-COM-MUON-2017-040}}.
\bibitem{mmtp} J. ~Farah {\it et al,} Test of the Micromegas Trigger Processor with Cosmic Ray Muons.
\bibitem{tuna} A. N. Tuna. Studies of the ATLAS MDT and CSC hit rates using proton-proton collisions at 13 TeV. 
  \href{https://cds.cern.ch/record/2111365}{\color{blue}\underline{ATL-COM-MUON-2015-098}}.
\bibitem{tpsim} N.~Felt \it et al,} Diamond-paved roads and steaming soup: the architecture of an upgraded Micromegas trigger processor and its optimization tool.
  \href{https://cds.cern.ch/record/2302523}{\color{blue}\underline{ATL-COM-MUON-2018-003}}.
\bibitem{phase2} ATLAS Muon Spectrometer Phase-II Upgrade Technical Design Report.
 \href{https://cds.cern.ch/record/2270169/}{\color{blue}\underline{ATL-COM-MUON-2017-033}}.
\bibitem{utpc} 
%\bibitem{oldart} K.~DiPetrillo  {it et al,} ATL-COM-MUON-2014-069.
%\bibitem{koki} Simulation of the ATLAS New Small Wheel (NSW) System
% \href{http://cds.cern.ch/record/2265067}{\color{blue}\underline{ATL-MUON-SLIDE-2017-248}}.
%\bibitem{lhc} LHC Design Report. 
% \href{https://cds.cern.ch/record/782076}{\color{blue}\underline{CERN-2004-003}}.

\end{thebibliography}








